Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-06-02 Paper.Rmd
will this ever end?

>>>>

As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses. Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses. Guo et al. (2019) @guo2019 found out that people spent more time when evaluating negative reviews. This may suggest a linear interaction between Review Extremity and Review Length. Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low. And when a review is longer it is more helpful for negatively rated reviews than positively rated reviews. In this case, it is hypothesized that:

*H3: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*

Potential buyers may find more recent reviews helpful because they may want to get updated information on a product. This might especially be true for products which are on the market for more than a year. For instance, a laptop which was produced in 2018 could be a good choice for that year but for year 2021 it is probable that its features and specifications would be below average. A similar behavior might be possible for movies as well. However, this time reviewers might need to take their time to digest and evaluate the movie. A review which is carefully constructed may be posted later making it more recent compared to a review which was hastily written. Furthermore, some popular movies which are considered as classics may attract reviews even way later than they were first released. Since some websites may employ algorithms that may push newer reviews to the top in order to be able to increase the interaction on their platforms, these kind of reviews may attract more helpful votes. Thus, it is hypothesized that:

*H4: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*
